Clicks and Cliques

### 2018-12-23 papersoul.Rnw
update us map

Figure \ref{map} shows the communities location, most are from the East Coast of the United States. Size of the dot represents population. Detroit and Philadelphia are the biggest communities while Aberdeen and Milledgeville are the smallest.
\begin{figure}[hbpt]
\centering
<<mapita,dependson='data',echo=FALSE, fig.height=6,message=FALSE,warning=FALSE,warning=FALSE, cache=TRUE>>=
lon.lat <- read.table('lon.lat.txt',header=T)
library(ggmap)
library(mapproj)

mapp <- get_googlemap(location = 'united states', zoom = 4, maptype = "terrain")

aux.mer <- inner_join(lon.lat, 
                 select(census.data.new, QSB,pop100), 
                 by = c('Community'='QSB') )

aux.mer$cate[aux.mer$pop100 < 3] <- 1
aux.mer$cate[aux.mer$pop100 >= 3&aux.mer$pop100 < 8] <- 2
aux.mer$cate[aux.mer$pop100 >= 8 & aux.mer$pop100 < 20] <- 3
aux.mer$cate[aux.mer$pop100 >= 20] <- 4

p <- ggmap(mapp, extent = "device")
p + geom_point(data = aux.mer, mapping = aes(lon, lat), size = 6*aux.mer$cate, alpha = .4) + xlab('') + ylab('') + theme(axis.text.x = element_blank(), axis.text.y = element_blank())
@
  \caption{Location of the 26 communities analyzed, size of dot represent population. Only two communities on the west coast are included. \label{map}}
\end{figure}

@@

\begin{figure}[hbpt]
<<cluster.cen, dependson=c('data','corplot'), echo=FALSE,message=FALSE,warning=FALSE>>=

d2 <- census.data %>% 
  select(aveageF, prop1821, Bachelor.s.degree.or.higher., gini , own.rate , afri.prop, prop.new.entry, un.rate, prop.no.workers ) %>%
  dist()

hc2 <- hclust(d2, method = 'ward.D')

census.data %>%
   mutate(cl.2 = cutree(hc2, 4) ) %>%
     select(aveageF, prop1821, un.rate, Bachelor.s.degree.or.higher., gini , own.rate ,  prop.new.entry, afri.prop, prop.no.workers, cl.2) %>% 
  group_by(cl.2) %>%
  summarise_all(funs(mean)) %>%
  ungroup() %>%
  rename(Age.Fem = aveageF, Yr.1821 = prop1821, Unemp = un.rate, Bachelor = Bachelor.s.degree.or.higher., Gini = gini, Own.rate = own.rate, New.entry = prop.new.entry, Afri.pr= afri.prop, No.workers = prop.no.workers, cl.2 = cl.2) %>% 
  mutate(cl.2 = factor(cl.2)) %>%
  ggparcoord(columns = 2:10, scale = 'std',
             groupColumn = 'cl.2', showPoints = T, 
             order = c(3, 5, 6, 8, 2, 4, 10, 7, 9))  + 
  theme(axis.text.x = element_text(angle = 90, size = I(15))) + 
  labs(x = '', y = '') + 
  scale_color_brewer(type = 'qual', palette = 2, name = 'Group')

@
\caption{Parallel coordinate plot for community cluster means. \label{cluster.cen} }
\end{figure}

@@

\begin{figure}[hbpt]
<<corplot, echo=FALSE, dependson=c('data'),cache=TRUE, warning = FALSE>>=
# With Census data we want to describe communities

@@

\begin{figure}[hbpt]
<<cluster.plot1, dependson='cluster',echo=FALSE,message=FALSE,warning=FALSE,warning=FALSE,fig.height=6.5>>=

des.cl1 %>% 
  spread(vars,value) %>% 
  select(Q25, QCE2, Q7E, Q3B, Q8D, Q8A, Q15AA, Q7L, Q9, Q3A, Q15AB, Q6A, Q3C, Q6, Q7I, Q7F, Q7K, Q8F, Q7M, Q7D, QCE1, Q7A, Q7B, Q7C, Q8C, Q8E, Q8B, Q7H, Q18, Q7G, Q24,YEAR,cl.id) %>% 
  rename( Family = Q25, Refer = QCE2, Perfect = Q7E, Children = Q3B, Leader = Q8D, Proud = Q8A, Lead.Int. = Q15AA, Talented = Q7L, Job = Q9, Meet.People = Q3A, `5year.ahead` = Q15AB, School = Q6A, Reputation = Q3C, `5year.ago` = Q6, Care = Q7I, Senior = Q7F, Economy = Q7K, Satisfaction = Q8F, Health = Q7M, Find.Job = Q7D, Parks = QCE1, 
Beauty = Q7A, Roads = Q7B, Housing = Q7C, Night.Life = Q8C, Minorities = Q8E, Inmigrants = Q8B, Gay = Q7H, Safe = Q18, Colleges = Q7G, Friends = Q24, Clusters = cl.id) %>% 
 gather(vars, value, -Clusters,-YEAR) %>% 
  ggplot(aes(x = vars, y = value, color = Clusters, shape = Clusters), size = I(3)) + labs(x = "", y = "") +  geom_point(size = I(2))  + geom_line(aes(group = Clusters)) + 
  facet_wrap(~YEAR, nrow = 3) + theme(axis.text.x = element_text(angle = 90, size = I(15)), legend.position = 'bottom' ) + scale_color_brewer(type='qual', palette='Paired')

@
\caption{Cluster mean points. Mean values for all the variables used to create the clusters in every year. \label{para}}
\end{figure}

@@

\begin{figure}[hbpt]
<<cluster.plot2, dependson='data',echo=FALSE, fig.height=4,message=FALSE,warning=FALSE,warning=FALSE,fig.height=6.5>>=

soul.red2 %>%  rename(Cluster.ID = cl.id ) %>% 
prodplot(PROJWT ~ CCEGRP2 + Cluster.ID + YEAR, divider = c("vspine", "hspine",'vspine'), subset = level == 2) + aes(fill = CCEGRP2) + theme(legend.position = 'bottom', legend.title = element_blank(),axis.title.y = element_blank()) + scale_fill_brewer(type='seq', palette = 1)

@@

### VARIFICAR NOMBRES REPETIDOS EN SVYVAR !!!!!!!
life <- svyby(~prop.res + QD1 + CCE, ~QSB, des.wt, svymean, keep.var = TRUE, na.rm = T)
lifevar <- svyby(~prop.res + CCE, ~QSB, des.wt, svyvar, keep.var = TRUE, na.rm = T)
lifevar$rho <- with(lifevar, V2/sqrt(V1*V4))

ggplot(data = life, aes(x = prop.res, y = QSB), size = I(4)) + geom_point() +
labs(y = '', x ='Proportion of lifetime living in the community') + 
  theme(axis.text.y = element_text( size=I(10)))
@
\caption{Dot chart of communities sorted from top to bottom by attachment against the mean proportion of lifetime spent in the current community (stay). Communities where most of people are living longer are the less attached ones. \label{stay}}
\end{figure}

<<life.tab, dependson=c('corplot','life'),echo=FALSE, results='asis', cache=FALSE, warning=FALSE>>=
# check correlation for prop.new.entry, should be 0.13
rho <- with(life, round(cor(CCE, prop.res),2) )

cors %>%  
  filter(vars %in% c("Prop.new.entry", "Average.years.rent.in.community", "Aver.years.own.in.community") &  type =='Attached' ) %>% 
  select(vars, vv) %>% rename(cor = vv) %>%
  bind_rows(data.frame(vars = 'stay', cor = rho)) %>% 
  mutate(Data =  c(rep('Census Bureau', 3), 'Knight-Gallup data'), 
         Description = c( 'Average years owning the current home', 
                          'Average years renting in current home', 
                          'Prop. of people not borned in the community', 
                          'Proportion of age in current comunity')) %>% 
  rename(Correlation = cor) %>% 
  select(Data, Description, Correlation) %>% 
  xtable( caption='Correlation with attachment', label='lifetab') %>% 
  print( caption.placement = 'top', include.rownames = FALSE)

@@

<<moving, dependson='data', echo=FALSE,results='asis', cache=FALSE>>=
soul %>% 
  mutate(Q5 = recode_factor(Q5, "(DK)" = "Non Response", 
    "(Refused)" = "Non Response",
    "Move outside of (answer from Sc) but stay in the state" = "Move from your neighborhood",
    "Move outside of this communitybut stay in the state" = "Move from your neighborhood",
    "Move to another city and state altogether" = "Move from your neighborhood",
    "Move to another neighborhood in (answer from Sc)" = "Move from your neighborhood", 
    "Move to another neighborhood in this community" = "Move from your neighborhood")) %>%  
  filter(!is.na(PROJWT)) %>% 
  mutate(pr = PROJWT/3)  %>% 
  svydesign(ids =~1, strata =~QSB, weights =~pr, data = .) %>% 
  svyby(~Q5,~CCEGRP2, design = ., svymean,keep.var = FALSE, na.rm = T) %>% 
  ftable() %>% data.frame() %>% 
  mutate( Var2 = gsub('statistic.Q5', '', Var2) ) %>% 
  spread(CCEGRP2, Freq) %>%  
  xtable(caption = 'Willingness to move outside your neighborhood', label = 'move') %>% 
  print(caption.placement = 'top')

@@

\begin{figure}
<<life_seq, dependson=c('life'), echo=FALSE,fig.height=4,message=FALSE,warning=FALSE>>=
life %<>% life %>%
  mutate(QSB = factor(QSB, levels = rev(levels(QSB))))

lifevar %>% data.frame() %>%  select(-starts_with('se')) %>%
  ggplot(aes(x = QSB, ymax = rho, ymin = 0)) +
  geom_linerange(size = I(2)) +
  labs(x = '',  y = "Correlation") +
  theme(axis.text.y = element_text( size = I(10) ), axis.text.x = element_text(size = I(10), angle = 90), axis.title.x = element_text(size = I(25)))

@
\caption{ Bar chart of correlations between attachment and lifetime living in the community within each community (ordered by attachment level). Only few communities shows negative correlation between attachment and lifetime living there. \label{wrho}}
\end{figure}

@@

ggplot(data = rhos.m, aes(x = YEAR, y = value)) + 
  labs(x = "", y = "", title = 'Evolution of Attachment-Economy correlation and GDP') +
  geom_line() + geom_point() +
  facet_grid(facets = variable~., scales = 'free') + 
  ggtitle('Evolution of Attachment-Economy correlation and GDP')

@
\caption{Attachment vs economic dimension. Top panel shows the correlation between attachment and economy index against time. Bottom panel shows the GDP growth rate against years. \label{eco}}
\end{figure}

>>>>

Figure \ref{map} shows the communities location, most are from the East Coast of the United States. Size of the dot represents population. Detroit and Philadelphia are the biggest communities while Aberdeen and Milledgeville are the smallest.
\begin{figure}[hbpt]
\centering
<<mapita,dependson='data',echo=FALSE, fig.height=6,message=FALSE,warning=FALSE,warning=FALSE, cache=TRUE>>=
lon.lat <- read.table('lon.lat.txt',header=T) %>% 
  inner_join( select(census.data, QSB, pop100), by = c('Community'='QSB') ) %>% 
  mutate( popSize = cut(pop100, 
                        breaks = c(0, 3, 8, 20, 50),
                        labels = 1:4) )

us <- map_data("state")

ggplot() + 
  geom_path(data = us, aes(long, lat, group=group), color = 'grey' ) +
  geom_point(data=lon.lat, aes(x=lon, y=lat, size = pop100), alpha = .5) +
  xlab('') + ylab('') + 
  scale_size(range = c(5,20)) + 
  scale_color_brewer(type = 'seq') +
  theme(axis.text.x = element_blank(), axis.text.y = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        axis.text = element_blank(), 
        legend.position = 'none')
@
\caption{Geographical location of the 26 communities in the data, dot's size represents population. Only two communities on the west coast are included. \label{map}}
\end{figure}

@@

\begin{figure}[hbpt]
<<cluster.cen, dependson=c('data','corplot'), echo=FALSE,message=FALSE,warning=FALSE>>=
# var.cl2 <- colnames(census.data) %in% c("aveageF","prop1821", "Bachelor.s.degree.or.higher." , "gini" , "own.rate" , "afri.prop",'prop.new.entry','un.rate',"prop.no.workers" )
d2 <- census.data %>% select(aveageF, prop1821, Bachelor.s.degree.or.higher., gini , own.rate , afri.prop, prop.new.entry, un.rate, prop.no.workers ) %>% dist()

# d2 <- dist(census.data[, var.cl2])
hc2 <- hclust(d2, method = 'ward.D')
# census.data$cl.2 <- cutree(hc2, 4)

# Characterize the clusters with the numerical variables
nn <- c('cl.2', 'Age.Fem', '1821.Yr','Bachelor', 'Unemp','Gini','Own.rate', 'Afri.pr', 'No.workers', 'New.entry' )

census.data %>%
  mutate(cl.2 = cutree(hc2, 4) ) %>% 
  select( c(colnames(census.data)[var.cl2],'cl.2' ) ) %>% 
  group_by(cl.2) %>%
  summarise_all(funs(mean)) %>%
  setNames(nn) %>% ungroup() %>%
  mutate(cl.2 = factor(cl.2)) %>% 
  ggparcoord(columns = 2:10, scale = 'std', 
             groupColumn = 'cl.2', showPoints = T, 
             order = c(4, 10, 2, 7, 8, 6, 3,5, 9))  + 
  theme(axis.text.x = element_text(angle = 90, size = I(15))) + 
  labs(x = '', y = '') + 
  scale_color_brewer(type = 'qual', palette = 2, name = 'Group')

  # c(3, 4, 6, 10, 2, 5, 9, 7, 8)
@
\caption{Parallel coordinate plot for community cluster means. \label{cluster.cen} }
\end{figure}

@@

\begin{figure}[hbpt]
<<corplot, echo=FALSE, dependson=c('data'),cache=TRUE>>=
# With Census data we want to describe communities

@@

\begin{figure}[hbpt]
<<cluster.plot1, dependson='cluster',echo=FALSE,message=FALSE,warning=FALSE,warning=FALSE,fig.height=6.5>>=
lab <- c('Family','Refer','Perfect','Children','Leader','Proud', 'Lead. Int.','Talented','Job','Meet.People','
         5year.ahead', 'School','Reputation','5year.ago', 'Care', 'Senior','Economy','Satisfaction','Health',
         'Find.Job', 'Parks','Beauty','Roads','Housing','Night.Life', 'Minorities', 'Inmigrants', 'Gay', 'Safe','Colleges', 'Friends')

aux2 <- subset(des.cl1, variable %in% levels(des.cl1$variable)[1:31])
aux2$variable <- factor(aux2$variable)
aux2$var2 <- as.integer(aux2$variable)
colnames(aux2)[1] <- 'Clusters'

#,main='Mean Value Selected Variables Used in the K-means Cluster'
qplot(data = aux2, var2, value, color = Clusters,shape = Clusters,xlab = '', ylab = '',size = I(3)) +geom_line(size = I(.5)) + facet_wrap(~YEAR,nrow = 3) + theme(axis.text.x = element_text(angle = 90, size = I(15)), legend.position = 'bottom' ) + scale_x_discrete(breaks = 1:31, labels = lab) + scale_color_brewer(type='qual', palette='Paired')
@
\caption{Cluster mean points. Mean values for all the variables used to create the clusters in every year. \label{para}}
\end{figure}

@@

\begin{figure}[hbpt]
<<cluster.plot2, dependson='data',echo=FALSE, fig.height=4,message=FALSE,warning=FALSE,warning=FALSE,fig.height=6.5>>=
ind <- colnames(soul.red2) == 'cl.id'
colnames(soul.red2)[ind] <- 'Cluster.ID'

prodplot(soul.red2, PROJWT ~ CCEGRP2+ Cluster.ID + YEAR, divider=c("vspine", "hspine",'vspine'), subset = level == 2)+aes(fill = CCEGRP2) + theme(legend.position = 'bottom', legend.title = element_blank(),axis.title.y=element_blank()) + scale_fill_brewer(type='seq', palette=1)

@@

### VARIFICAR NOMBRES REPETIDOS EN SVYVAR !!!!!!!
life <- svyby(~prop.res+QD1+CCE, ~QSB, des.wt, svymean, keep.var=TRUE, na.rm=T)
lifevar <- svyby(~prop.res+CCE, ~QSB, des.wt, svyvar, keep.var=TRUE, na.rm=T)
lifevar$rho <- with(lifevar, V2/sqrt(V1*V4))

qplot(data=life, x=prop.res, y=QSB, size=I(4), ylab='',xlab='Proportion of lifetime living in the community')+theme(axis.text.y = element_text( size=I(10)))
@
\caption{Dot chart of communities sorted from top to bottom by attachment against the mean proportion of lifetime spent in the current community (stay). Communities where most of people are living longer are the less attached ones. \label{stay}}
\end{figure}

<<life.tab, dependson=c('corplot','life'),echo=FALSE, results='asis', cache=FALSE>>=
aux1 <- subset(dat.cor, vars %in% c("prop.new.entry","av.rent","av.own" ) & type=='Attached')[,1:2]

rho <- with(life, round(cor(CCE, prop.res),2) )

aux2   <- data.frame(vars='stay', cor=rho)
aux3 <- rbind(aux1,aux2)
description <-c('Average years renting in current home', 'Average years owning the current home',
              'Prop. of people not borned in the community', 'Proportion of age in current comunity')
data.source <- c(rep('Census Bureau', 3), 'Knight-Gallup data')
tab <- data.frame(Data=data.source,Description=description,Correlation=aux3$cor)
row.names(tab) <- NULL
tab <- xtable(tab, caption='Correlation with attachment', label='lifetab')
print(tab, caption.placement='top')
@

@@

<<moving, dependson='data', echo=FALSE,results='asis', cache=FALSE>>=
levels(soul$Q5)[1:2] <- 'Non Response'
levels(soul$Q5)[2:6] <- 'Move from your neighborhood'
soul$Q5 <- factor(soul$Q5)

pr <- with(subset(soul, !is.na(PROJWT) ), PROJWT/3)
des.pro <- svydesign(ids=~1, strata=~QSB, weights=~pr, data=subset(soul, !is.na(PROJWT) ) )

tab <- svyby(~Q5,~CCEGRP2, des.pro, svymean,keep.var=FALSE, na.rm=T)
tab <- round(100*ftable(tab), 2)

dt <- data.frame(matrix(tab[1:9], ncol=3))
rownames(dt) <- levels(soul$Q5)
colnames(dt) <- levels(soul$CCEGRP2)
dt <- xtable(dt, caption='Willingness to move outside your neighborhood', label='move')
print(dt, caption.placement='top')

@@

\begin{figure}
<<life_seq, dependson=c('life'), echo=FALSE,fig.height=4,message=FALSE,warning=FALSE>>=
life$QSB <- with(life, factor(QSB, levels = rev(levels(QSB))))

lifevar %>% data.frame() %>%  select(-starts_with('se')) %>%
  qplot(data=., x=QSB,ymax=rho,ymin=0, xlab='',geom='linerange', ylab='Correlation',size=I(2))  + theme(axis.text.y = element_text( size=I(10) ),axis.text.x = element_text(size=I(10), angle=90),axis.title.x = element_text(size=I(25)))
@
\caption{ Bar chart of correlations between attachment and lifetime living in the community within each community (ordered by attachment level). Only few communities shows negative correlation between attachment and lifetime living there. \label{wrho}}
\end{figure}

@@

qplot(data=rhos.m, x=YEAR, y=value,xlab='',ylab='', geom=c('point','line')) +facet_grid(facets=variable~.,scales='free')+ ggtitle('Evolution of Attachment-Economy correlation and GDP')
@
\caption{Attachment vs economic dimension. Top panel shows the correlation between attachment and economy index against time. Bottom panel shows the GDP growth rate against years. \label{eco}}
\end{figure}
